ps4_models

### 2020-10-27 test.Rmd
more stuff

```{r}
raw_data <- read_dta("inputs/data/usa_00001.dta")
# Add the labels
raw_data <- labelled::to_factor(raw_data)

# Just keep some variables that may be of interest (change 
# this depending on your interests)
names(raw_data)

>>>>

```{r}
raw_data <- read_dta("inputs/data/usa_00001.dta")
# Add the labels
raw_data <- labelled::to_factor(raw_data)
```

```{r}
# Just keep some variables that may be of interest (change 
# this depending on your interests)
names(raw_data)
